Urban Diversity Through an Information-Theoretic Lens

### 2016-08-31 5_figs.Rmd
minor updates to slides and paper

first <- method_illustration('Detroit', vmax = 6)
second <- method_illustration('Philadelphia', vmax = 6)

gA <- ggplotGrob(first)
gB <- ggplotGrob(second)
g <- gridExtra::cbind.gtable(gA, gB, size = "max")

grid.draw(g)

ggsave('figs/method_illustration.png', g, width = 8, height = 5)

>>>>

# first <- method_illustration('Detroit', vmax = 6)
# second <- method_illustration('Philadelphia', vmax = 6)
# 
# gA <- ggplotGrob(first)
# gB <- ggplotGrob(second)
# g <- gridExtra::cbind.gtable(gA, gB, size = "max")
# 
# grid.draw(g)
# 
# ggsave('figs/method_illustration.png', g, width = 8, height = 5)

### 2016-08-31 slides.tex
tech revisions
minor updates to slides and paper

\documentclass{beamer}
\usepackage{standalone}
\usepackage{import}
\usepackage{csquotes}
\usepackage{appendixnumberbeamer}
\usepackage{csvsimple}
\usepackage{bbding}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{etoolbox}
\usepackage{hyperref}

\usetheme{metropolis}
\metroset{block=fill}
\metroset{progressbar=frametitle}
\setbeamertemplate{bibliography item}{}
\setbeamertemplate{caption}{\raggedright\insertcaption\par}

\makeatletter
\def\beamer@framenotesbegin{% at beginning of slide
  \gdef\beamer@noteitems{}%
  \gdef\beamer@notes{{}}% used to be totally empty.
}
\makeatother

\title{Urban Diversity Through an Information-Theoretic Lens}
\date{\today}
\author{Phil Chodrow}
\institute{MIT Human Mobility and Networks Laboratory \alert| Operations Research Center}

% \includeonly{tex/slides/intro} will want this later.

@@

	\end{frame}
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\iflong
	\begin{frame}\frametitle{Albuquerque: Low diversity, fairly even, high exposure}
		\begin{figure}
			\includegraphics[width=\textwidth]{external_figs/albuquerque_dot.png}
			\caption{\textit{Image Copyright, 2013, Weldon Cooper Center for Public Service, Rector and Visitors of the University of Virginia (Dustin A. Cable, creator)}}
		\end{figure}
	\end{frame}
	\fi
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\iflong
	\begin{frame}\frametitle{Detroit: High diversity, highly uneven, low exposure}
		\begin{figure}
			\includegraphics[width=\textwidth]{external_figs/detroit_dot.png}
			\caption{\textit{Image Copyright, 2013, Weldon Cooper Center for Public Service, Rector and Visitors of the University of Virginia (Dustin A. Cable, creator)}}
		\end{figure}
	\end{frame}
	\fi
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\iflong
	\begin{frame}\frametitle{Philadelphia: High diversity, highly uneven, high exposure}
		\begin{figure}
			\includegraphics[width=\textwidth]{external_figs/philly_dot.png}
			\caption{\textit{Image Copyright, 2013, Weldon Cooper Center for Public Service, Rector and Visitors of the University of Virginia (Dustin A. Cable, creator)}}
		\end{figure}
	\end{frame}
	\fi
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Diversity and Information Theory}
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\iflong
		\begin{frame}\frametitle{Why Information Theory?}
			Information theory quantifies concepts like uncertainty and predictability. Why use it for studying diversity? 
			\onslide<2->{
				\begin{block}{Core Insight}
					\begin{itemize}
						\item Complex systems allow \textbf{some} prediction...
						\item ...But good prediction is \textbf{hard}.
					\end{itemize}
				\end{block}
			}
			\onslide<3>{
				\textbf{Examples of prediction:}
				\begin{itemize}
					\item If you pick a random person from a city, is it hard to guess their race? ``Yes'' $\implies$ more diverse city. 
					\item Does it help if you tell me where they live? ``Yes'' $\implies$ more uneven city. 
				\end{itemize}
			}
		\end{frame}

@@

	\iflong
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\begin{frame}\frametitle{Entropy as Global Diversity}
		Let $p(X,Y)$ be the joint distribution of location $X$ and race $Y$. The marginal distribution of race alone is $p(Y) = \sum_{x \in \mathcal{X}} p(x,Y)$. 
		\begin{block}{Entropy}
			\begin{equation*}
				H(Y) \triangleq - \mathbb{E}_Y[\log p(Y)] = -\sum_{y \in \mathcal{Y}} p(Y)\log p(Y)
			\end{equation*}
		\end{block}
		\onslide<2->{\begin{align*}
			H(Y) = 0 &\implies \text{ city is monoracial} \\
			H(Y) = \log \left|\mathcal{Y}\right| &\implies \text{ all races are represented equally}
		\end{align*}}
	\end{frame}
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\begin{frame}\frametitle{Mutual Information as Evenness}
		The mutual information quantifies the degree of dependence between two random variables.
		\begin{block}{Mutual Information}
			\begin{align*}
				I(X,Y) &\triangleq \mathbb{E}_{X,Y}\left[\log \frac{p(X,Y)}{p(X)p(Y)}\right] \\
				&= \int_{\mathbb{R}^n} \; d^nx  \sum_{y \in \mathcal{Y}} p(x,Y) \log \frac{p(x,Y)}{p(x)p(Y)}\;.
			\end{align*}	
		\end{block}
		\onslide<2->{\begin{align*}
			I(X,Y) = 0 &\implies \text{ location and race are independent} \\
			I(X,Y) = \log \left|Y\right| &\implies \text{ location determines race}
		\end{align*}}
	\end{frame}
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\begin{frame}\frametitle{Spatializing Mutual Information}
		Let $I_r(x_0)$ be local the mutual information between $X$ and $Y$, restricted to a small area of radius $r$ centered at $x_0$. Think of this as the \textbf{spatial variation of racial trends in a small area.} 
		\onslide<2->{
			\begin{block}{Theorem}
				Under appropriate regularity conditions, for small $r$,
				\begin{equation*}
					\frac{I_r(x_0)}{r^2} \cong \frac{1}{4} \text{trace } J_Y(x_0)\;, \tag{proof on request}
				\end{equation*}
				where $J_Y(x_0)$ is the Fisher information in $Y$ about $x_0$ \nocite{Amari2000}
			\end{block}
		}
		\onslide<3->{
			\alert{Significance}: the local information $I_r(x_0)$ is related to an intrinsic statistical measure $J_Y(x)$ \emph{that is independent of the spatial resolution $r$}.
		}

@@

	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\begin{frame}\frametitle{Mean Local Information Measures Spatial Exposure}
		We're interested in the average value of local information:

>>>>

\documentclass{beamer}
\usepackage{pc_slides}

\title{Urban Diversity Through an Information-Theoretic Lens}
\date{\today}
\author{Phil Chodrow}
\institute{MIT Human Mobility and Networks Laboratory \alert|\alert| Operations Research Center}

@@

	\end{frame}
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

	\begin{frame}\frametitle{Albuquerque: Low diversity, fairly even, high exposure}
		\begin{figure}
			\includegraphics[width=\textwidth]{external_figs/albuquerque_dot.png}
			\caption{\textit{Image Copyright, 2013, Weldon Cooper Center for Public Service, Rector and Visitors of the University of Virginia (Dustin A. Cable, creator)}}
		\end{figure}
	\end{frame}

	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

	\begin{frame}\frametitle{Detroit: High diversity, highly uneven, low exposure}
		\begin{figure}
			\includegraphics[width=\textwidth]{external_figs/detroit_dot.png}
			\caption{\textit{Image Copyright, 2013, Weldon Cooper Center for Public Service, Rector and Visitors of the University of Virginia (Dustin A. Cable, creator)}}
		\end{figure}
	\end{frame}

	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

	\begin{frame}\frametitle{Philadelphia: High diversity, highly uneven, high exposure}
		\begin{figure}
			\includegraphics[width=\textwidth]{external_figs/philly_dot.png}
			\caption{\textit{Image Copyright, 2013, Weldon Cooper Center for Public Service, Rector and Visitors of the University of Virginia (Dustin A. Cable, creator)}}
		\end{figure}
	\end{frame}

	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Diversity and Information Theory}
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\iflong
		\begin{frame}\frametitle{Why Information Theory?}
			Information theory quantifies concepts like uncertainty and predictability. Why use it for studying diversity? 
			\onslide<2->{
				\begin{block}{Core Insight}
					\begin{itemize}
						\item Complex systems allow \textbf{some} prediction...
						\item ...But good prediction is \textbf{hard}.
					\end{itemize}
				\end{block}
			}
			\onslide<3>{
				\textbf{Examples of prediction:}
				\begin{itemize}
					\item If you pick a random person from a city, is it hard to guess their race? ``Yes'' $\implies$ more diverse city. 
					\item Does it help if you tell me where they live? ``Yes'' $\implies$ more uneven city. 
				\end{itemize}
			}
		\end{frame}

@@

	\iflong
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\begin{frame}\frametitle{Entropy as Global Diversity}
		Let $p(X,Y)$ be the joint distribution of location $X$ and race $Y$. The marginal distribution of race alone is $p(Y) = \sum_{x \in \mathcal{X}} p(x,Y)$. 
		\begin{block}{Entropy}
			\begin{equation*}
				H(Y) \triangleq - \mathbb{E}_Y[\log p(Y)] = -\sum_{y \in \mathcal{Y}} p(Y)\log p(Y)
			\end{equation*}
		\end{block}
		\onslide<2->{\begin{align*}
			H(Y) = 0 &\implies \text{ city is monoracial} \\
			H(Y) = \log \left|\mathcal{Y}\right| &\implies \text{ all races are represented equally}
		\end{align*}}
	\end{frame}
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\begin{frame}\frametitle{Mutual Information as Evenness}
		The mutual information quantifies the degree of dependence between two random variables.
		\begin{block}{Mutual Information}
			\begin{align*}
				I(X,Y) &\triangleq \mathbb{E}_{X,Y}\left[\log \frac{p(X,Y)}{p(X)p(Y)}\right] \\
				&= \int_{\mathbb{R}^n} \; d^nx  \sum_{y \in \mathcal{Y}} p(x,y) \log \frac{p(x,y)}{p(x)p(y)}\;.
			\end{align*}	
		\end{block}
		\onslide<2->{\begin{align*}
			I(X,Y) = 0 &\implies \text{ location and race are independent} \\
			I(X,Y) = \log \left|Y\right| &\implies \text{ location determines race}
		\end{align*}}
	\end{frame}
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\begin{frame}\frametitle{Spatializing Mutual Information}
		Let $I_r(x_0)$ be local the mutual information between $X$ and $Y$, restricted to a small area of radius $r$ centered at $x_0$. Think of this as the \textbf{spatial variation of racial trends in a small area.} 
		\onslide<2->{
			\begin{block}{Theorem}
				Under appropriate regularity conditions, for small $r$,
				\begin{equation*}
					\frac{I_r(x_0)}{r^2} \cong \frac{1}{4} \text{trace } J_Y(x_0)\;, 
				\end{equation*}
				where $J_Y(x_0)$ is the Fisher information in $Y$ about $x_0$ \nocite{Amari2000}
			\end{block}
		}
		\onslide<3->{
			\alert{Significance}: the local information $I_r(x_0)$ is related to an intrinsic statistical measure $J_Y(x)$ \emph{that is independent of the spatial resolution $r$}.
		}

@@

	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\begin{frame}\frametitle{Mean Local Information Measures Spatial Exposure}
		We're interested in the average value of local information as captured by $J_Y(X)$:

### 2016-08-31 tex/paper/intro.tex
minor updates to slides and paper

	The approach we develop is grounded in information measures of spatial demographic structure. Information theory maps the physical concept of structure to the epistemic concept of predictability. A complex system has enough structure to be at least partially predictable, but enough variability to make prediction challenging. Information-theoretic concepts have already been introduced in the study of cities, finding application in urban planning problems, in predicting population distributions, and in quantifying difference between neighborhoods \cite{Royal2014,Batty1974,Batty1976,Battya,Bettencourt2015,Webber1979}. Attractive features of information measures include their deep relationship to statistical inference \cite{Cover1991,Csiszzr2004}, their generalizability to a wide variety of phenomena, and their conceptual linkage of cities with the methods of statistical physics. In the context of the measurement of urban demographic structure, information measures provide answers to questions such as: 
	\begin{enumerate}
		\item Supposing you choose an individual randomly from a city, how accurately could I guess their race? 
		\item Supposing you then told me where that person lived within the city, how much would this new information increase my accuracy? 
	\end{enumerate}
	The following considerations connect these questions to the measurement of diversity and structure. If I can guess a random individual's race with 100\% accuracy given no information, then it must be the case that the city is monoracial; increased diversity reduces my ability to guess. If knowing where a person lives dramatically increased my ability to guess, then there must be substantial structural dependence of demographics on space, a prerequisite of segregation.

	We make two primary contributions. The first is to the field of quantitative segregation studies in sociology. We formulate the \emph{mean local information} $J(X,Y)$ as a measure of spatiosocial structure. We then show that this novel measure, in concert with the mutual information $I(X,Y)$, comprise a unified, spatially-aware methodology for the measurement of diversity and segregation. These metrics possess many of the traditionally desirable properties of sociological indices, and can be easily computed from open data such as that provided by the U.S. Census. Our second contribution is to provide a simple, theoretically-motivated, and computationally-tractable method for agglomerating spatio-social data into ``natural neighborhoods'' across which demographic trends are approximately constant. This method has multiple applications. Sociologists can use this agglomeration procedure to study racially coherent neighborhoods, rather than the partially-arbitrary administrative boundaries such as those produced by the U.S. Census. Computational urban planners can use the method for \emph{dimension-reduction}, in which a large data set is made more computationally tractable while preserving spatio-social relationships of interest. Finally, urban physicists may be interested in the scaling behavior of the mutual information across different levels of aggregation in analogy with coarse-graining in statistical mechanics \cite{Bettencourt2015}. The hierarchical character of agglomerative clustering defines a non-arbitrary way to perform this aggregation.

\subsection*{Structure of the Essay}
	In Section 2, we motivate and develop the two core components of our mathematical framework. The first of these is the mean local information $J(X,Y)$, a measure of the intrinsic spatial complexity of a compositional phenomenon. In the context of racial trends in cities, the mean local information measures the granularity of racial neighborhood structure. It is low in a city like Detroit, which consists of a few large, monolithic tracts of constant racial composition. It is high in a city like Philadelphia, in which many (spatially) smaller neighborhoods are knit together in an intricate patchwork. The second component of our mathematical framework is a simple algorithm for identifying clusters that are both spatially and compositionally coherent through agglomerative hierarchical clustering and greedy information maximization. In the context of race in cities, this algorithm may be viewed as an automated means to identify ``natural'' neighborhoods.

@@

	Section 4 is a discussion of our findings and prospects for future work. We have also provided an Appendix, which includes links to software repositories, ommitted mathematical notes, and specifications of computational procedures used.

>>>>

	The approach we develop is grounded in information measures of spatial demographic structure. Information theory maps the physical concept of structure to the epistemic concept of predictability. A complex system has enough structure to be at least partially predictable, but enough variability to make prediction challenging. Information-theoretic concepts have already been introduced in the study of cities, finding application in urban planning problems, in predicting population distributions, and in quantifying difference between neighborhoods \cite{Royal2014,Batty1974,Batty1976,Battya,Bettencourt2015,Webber1979}. Attractive features of information measures include their deep relationship to statistical inference \cite{Cover1991,Csiszzr2004}, their generalizability to a wide variety of phenomena, and their conceptual linkage of cities with the methods of statistical physics. In the context of the measurement of urban demographic structure, information measures provide answers to questions such as: 
	\begin{enumerate}
		\item Supposing you choose an individual randomly from a city, how accurately could I guess their race? 
		\item Supposing you then told me where that person lived within the city, how much would this new information increase my accuracy? 
	\end{enumerate}
	These questions are intimately connected with the measurement of diversity and structure. If I can guess a random individual's race with 100\% accuracy given no additional information, then it must be the case that the city is monoracial; increased diversity reduces my ability to guess. If knowing where a person lives dramatically increased my ability to guess, then there must be substantial structural dependence of demographics on space, reflecting a kind of spatial segregation.

	We make two primary contributions. The first is to the theory of segregation measurement in sociology. We formulate the \emph{mean local information} $J(X,Y)$ as a measure of spatiosocial structure. We then show that this novel measure, in concert with the mutual information $I(X,Y)$, provides a mathematically unified, operationally interpretable, and spatially-aware methodology for the measurement of diversity and segregation. These metrics possess many of the traditional virtues of segregation indices and can be easily computed from open data such as that provided by the U.S. Census. Our second contribution is to provide a simple, theoretically-motivated, and computationally-tractable method for agglomerating spatio-social data into ``natural neighborhoods'' across which demographic trends are approximately constant. This method has multiple applications. Sociologists can use this agglomeration procedure to study racially coherent neighborhoods, rather than the partially-arbitrary administrative boundaries such as those produced by the U.S. Census. Computational urban planners can use the method for \emph{dimension-reduction}, in which a large data set is made more computationally tractable while preserving spatio-social relationships of interest. Finally, urban physicists may be interested in the scaling behavior of the mutual information across different levels of aggregation in analogy with coarse-graining in statistical mechanics \cite{Bettencourt2015}. The hierarchical character of agglomerative clustering defines a non-arbitrary way to perform this aggregation.

\subsection*{Structure of the Essay}
	In Section 2, we motivate and develop the two core components of our mathematical framework. The first of these is the mean local information $J(X,Y)$, a measure of the intrinsic spatial complexity of a compositional phenomenon. In the context of racial trends in cities, the mean local information measures the granularity of racial neighborhood structure. It is low in a city like Detroit, which consists of a few large, monolithic tracts of constant racial composition. It is high in a city like Philadelphia, in which many (spatially) smaller neighborhoods are knit together in an intricate patchwork. We develop the mathematics of the mean local information and describe its properties. The second component of our mathematical framework is a simple algorithm for identifying clusters that are both spatially and compositionally coherent through agglomerative hierarchical clustering and greedy information maximization. In the context of race in cities, this algorithm may be viewed as an automated means to identify ``natural'' neighborhoods.

@@

	Section 4 is a discussion of our findings and prospects for future work. We have also provided an Appendix, which includes links to software repositories, mathematical proofs, and specifications of computational procedures used.
